Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-14 manuscript/ERL_global_C_SI.Rmd
starting some rearrangement
fixed SI knitting problem

                  \usepackage{setspace}\onehalfspacing
                  \usepackage{lineno}\linenumbers

---
\raggedright

@@

\newpage
## Figure S1. Age trends and biome differences for $NEP$

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/NEP.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/GPP.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/NPP.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP_woody.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP_stem.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP_foliage.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/ANPP_litterfall.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_coarse.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/BNPP_fine.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/R_eco.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/R_root.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/R_soil.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/R_het_soil.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_ag.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_ag_woody.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_foliage.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_root.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_root_coarse.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/biomass_root_fine.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/deadwood.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/deadwood_standing.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/deadwood_down.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/age_trends/organic.layer.png")
```

>>>>

                  \usepackage{setspace}\onehalfspacing

---

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
path_to_dir <- dirname(dirname(getwd())) # get path to repo

# MOVE FIGURE FILES (Need to do this because I got an error when using the absolute path to call figures. However, it's not working at the moment, so did manual copy paste. )

#C cycle diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/C_cycle_diagrams/", full.names = TRUE))) # first remove old files

#flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/", full.names = TRUE)
#file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/C_cycle_diagrams/")

#Age diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/age_trends/", full.names = TRUE))) # first remove old files

#flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForC-db/ForC/figures/age_trends/", full.names = TRUE)
#file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/age_trends/")

# FIGURE NUMBERS

#SI
diagram_TrB_young= "S1"
diagram_TeB_young= "S2"
diagram_TeN_young= "S3"
diagram_BoN_young= "S4"
NEP_fig= "S5"
GPP_fig= "S6"
NPP_fig= "S7"
ANPP_fig= "S8"
ANPP_woody_fig= "S9"
ANPP_stem_fig= "S10"
ANPP_foliage_fig= "S11"
ANPP_litterfall_fig= "S12"
BNPP_fig= "S13"
BNPP_coarse_fig= "S14"
BNPP_fine_fig= "S15"
R_eco_fig= "S16"
R_root_fig= "S17"
R_soil_fig= "S18"
R_het_soil_fig= "S19"

```

\raggedright

@@

\newpage
## Figure `r NEP_fig`. Age trends and biome differences for $NEP$

@@

  knitr::include_graphics("tables_figures/age_trends/NEP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/GPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/NPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_woody.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_stem.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_foliage.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/ANPP_litterfall.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_coarse.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/BNPP_fine.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_eco.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_root.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_soil.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/R_het_soil.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_ag.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_ag_woody.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_foliage.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_coarse.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/biomass_root_fine.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_standing.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/deadwood_down.png")
```

@@

  knitr::include_graphics("tables_figures/age_trends/organic_layer.png")
```
